Coherent optical association of a single molecule

### 2020-10-30 paper.tex
WIP: address Jons comments
* Figure label position
* Word tweak
* Legend
* Y label for wavefunction probability density

To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency
and scattering rate at different detunings from the atomic threshold
taking into account of all states of
the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011}
and the continuum~\cite{Liu2017}.
The excited atomic continuum is particularly important for the target molecular state.
The sum of the squares of the wavefunction overlap
between the target weakly-bound molecular state
and all the excited molecular intermediate states considered
\todo{all vibrational states} is only about $0.02$,
suggesting that there is significant matrix element
between the target molecular state and the excited atomic continuum (See SM).
This calculation shows that the ratio of the Raman Rabi rate to scattering rate
can be made larger for more deeply bound states compared to weakly-bound states
at a cost of a smaller Raman Rabi frequency
(Fig.~\ref{f-theory}b, full result in SM \todo{proper cite})
As a result, we choose the $v'=0$ of $c^3\Sigma^+(\Omega = 1)$ as an intermediate state
to drive the Raman transition. % (mention the trend, also v'=12 will work as similarly as v'=0)

@@

In order to calculate the matrix element ratio,
we now need to extract the up leg Rabi frequency, $ \Omega_a $.
We do this by measuring the dependencies of the Raman Rabi frequency,
which depends on both $\Omega_m$ and $\Omega_a$.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power
due to the change in the atomic wavefunction caused by
tighter confinement at higher power (Fig.~\ref{f-det}b).
Thus, as discussed before, for weakly interacting particles,
$\Omega_a$ scales as $ \omega_{\text{trap}}^{3/4}$ or $P^{0.375}$.
However, due to the strong interaction between the two atoms, this approximation breaks down.
Instead, coupled-channel calculation shows that the scaling
is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
which fits well to our experimental result.
Similar to the light shift, there is also a constant background component
and a $v'=0$ component in the Raman Rabi frequency that scales as $1/\Delta$.
The $v'=0$ component of the Raman Rabi frequency is
$2\pi\times170(4) ~\mathrm{Hz\cdot mW^{-1.29}}$,
or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $15 ~\mathrm{mW}$ tweezer power.
Together with the $\Omega_m$ measured above, the up leg Rabi frequency is
$2\pi \times 12.1(3)\mathrm{MHz}$.
This gives a Rabi frequency, and therefore matrix element ratio of $11.6(3)$,
which is in fact better than the theory prediction of $23.7$
and should not cause the ratio of the Raman Rabi frequency to scattering rate
from the $v'=0$ state to be higher than expected. \todo{split into two sentence}
Furthermore, we measure the natural linewidth of the $v'=0$ excited state to be no larger than $20 \mathrm{MHz}$ using photoassociation (PA) spectroscopy.
This suggests that the excited state linewidth should not cause
a stronger than expected scattering from $v'=0$ state either.

>>>>

To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency
and scattering rate at different detunings from the atomic threshold
taking into account of all states of
the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011}
and the continuum~\cite{Liu2017}.
The excited atomic continuum is particularly important for the target molecular state.
The sum of the squares of the wavefunction overlap
between the target weakly-bound molecular state
and all the excited molecular bound states is only about $0.02$,
suggesting that there is significant matrix element
between the target molecular state and the excited atomic continuum (See SM \todo{proper cite}).
This calculation shows that the ratio of the Raman Rabi rate to scattering rate
can be made larger for more deeply bound states compared to weakly-bound states
at a cost of a smaller Raman Rabi frequency
(Fig.~\ref{f-theory}b, full result in SM \todo{proper cite})
As a result, we choose the $v'=0$ of $c^3\Sigma^+(\Omega = 1)$ as an intermediate state
to drive the Raman transition. % (mention the trend, also v'=12 will work as similarly as v'=0)

@@

In order to calculate the matrix element ratio,
we now need to extract the up leg Rabi frequency, $ \Omega_a $.
We do this by measuring the dependencies of the Raman Rabi frequency,
which depends on both $\Omega_m$ and $\Omega_a$.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power
due to the change in the atomic wavefunction caused by
tighter confinement at higher power (Fig.~\ref{f-det}b).
Thus, as discussed before, for weakly interacting particles,
$\Omega_a$ scales as $ \omega_{\text{trap}}^{3/4}$ or $P^{0.375}$.
However, due to the strong interaction between the two atoms, this approximation breaks down.
Instead, coupled-channel calculation shows that the scaling
is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
which fits well to our experimental result.
Similar to the light shift, there is also a constant background component
and a $v'=0$ component in the Raman Rabi frequency that scales as $1/\Delta$.
The $v'=0$ component of the Raman Rabi frequency is
$2\pi\times170(4) ~\mathrm{Hz\cdot mW^{-1.29}}$,
or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $15 ~\mathrm{mW}$ tweezer power.
Together with the $\Omega_m$ measured above, the up leg Rabi frequency is
$2\pi \times 12.1(3)\mathrm{MHz}$.
This gives a Rabi frequency, and therefore matrix element ratio of $11.6(3)$,
which is in fact better than the theory prediction of $23.7$.
Therefore, this should not cause the ratio of the Raman Rabi frequency to scattering rate
from the $v'=0$ state to be higher than expected.
Furthermore, we measure the natural linewidth of the $v'=0$ excited state to be no larger than $20 \mathrm{MHz}$ using photoassociation (PA) spectroscopy.
This suggests that the excited state linewidth should not cause
a stronger than expected scattering from $v'=0$ state either.
